Forecasting the Changing Dynamics of US Energy Product Exports to OECD Markets: The Role of the Russian-Ukraine Conflict and Future Scenarios

### 2023-05-19 report_Tomo editinta.Rmd
nes reikejo

5.4 Comparison of ETS model against simple models
```{r Comparison of ETS model against simple models}
accuracy(crude_oil_fit) %>% 
  arrange(.model) %>% 
  select(.model, .type, RMSE, MAE, MAPE, MASE, RMSSE)
accuracy(additive_ets)
accuracy(auto_crude_ets)

>>>>

5.4 Comparison of ETS model against simple models
```{r Comparison of ETS model against simple models}
